---
title       : CAGR Stock
subtitle    : Identifying the low enough price for positive CAGR stock
author      : BL Khoo
job         : shiny app
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## CAGR and Stock Inflation concept

Stock price in general increase over time if the fundamental is right that is the business is profitable.
This means that the stock price growth can be modeld as the fundamental stock inflation.
This would result in the stock prices that can be modeled as $price = 2^t$.

Stock price (TA) then is a technical reflection of the fundamental (FA) and the sentiments and psychology of the market (PA). 

                                      TA = PA + FA

We created or assumed a model where the CAGR trend based on the linear regression is at the neutral or fair growth trend of the FA , which is the fundamental growth of the company. Any residual or error from the neutral CAGR then is considered as part of the PA or market price gyration due to fear or greed. 

The right price to have high probability gain would then be to identify the lowest points , given a line that is still parallel to the neutral regression line.


--- .class #id 

## Facilitating the price discovery via  simple shiny app and positive CAGR

The shiny app created is a simple visualization of the app to identify the price low enough based on historical trend and leverage on the linear regression model to do the estimation and use trend line offset.
This requires the application of the logarithm to the stock price to get  a straight line fit as far as possible particularly for  positive CAGR stock.

<img src=assets/img/shinyapp.png style="width: 750px">

``` {r, echo = FALSE , results=FALSE, warning=FALSE}

library(shiny)
library(quantmod)
library(lubridate)
library(date)
library(ggplot2)
library(grid)
library(scales)


getdata <- function(ticker) {
  
  symbol <<- ticker
  stk <<- getSymbols(ticker,auto.assign=FALSE)
  names(stk)[1] <<-"open"
  names(stk)[2] <<-"high"
  names(stk)[3] <<-"low"
  names(stk)[4] <<-"close"
  names(stk)[5] <<- "vol"
  names(stk)[6] <<- "price"
  sampleTimes <<- index(stk) 
  stk$year <<- year(index(stk))
  stk$mth <<- month(index(stk))
  
}

```

---
## Linear regression model on log Price.
The stock data is obtained from yahoo and consist of the following variables in time series dataset.
```{r echo=FALSE}

tail(stk,3)
```


a linear regression line is added and anothe offset LM line parallel to the LM line (indicated as black line) is created and allow the line to  shift by offset value. 
The idea is to have the line shifted to touch the lowest price points at least two of them to idenity the lowest support line.

--- 
## Plot illustrating the LM and offset LM lines
``` {r, echo=FALSE,warning=FALSE}



  
lplot <- function() 
{ ggplot( data=stk,aes(x=index(stk),y=price)) +
    geom_smooth(method="lm",se=FALSE,col="red") +
    geom_line() + labs(title="Log Price") + xlab("Year") +
    scale_y_continuous(trans = log2_trans(),
                       breaks = trans_breaks("log2", function(x) 2^x),
                       labels = trans_format("log2", math_format(2^.x)))  + ylab( expression(paste("Log"[2],' Price')))
  
  }
getdata("IBM")
p1 <- lplot()

lmplot <- function(offset=0)
{ p <- lplot()
  stk$o <- offset
  m <- lm(log(stk$price,base=2) ~ index(stk),offset=stk$o)
  l <- geom_abline(intercept = coef(m)["(Intercept)"], slope = coef(m)["index(stk)"],lwd=1)
  p + l
  
}

p2 <- lmplot(0.6)


multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)
  
  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)
  
  numPlots = length(plots)
  
  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                     ncol = cols, nrow = ceiling(numPlots/cols))
  }
  
  if (numPlots==1) {
    print(plots[[1]])
    
  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
    
    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
      
      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}

p2

```



---

## The End


